A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies

### 2018-08-31 for_submission/rvaught_2018.tex

\begin{document}
\title{A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies }
\author{Ryan Rickards Vaught}
\affiliation{Department of Astronomy, San Diego State University, San Diego, CA 92182}
\affiliation{Department of Physics, University of California, San Diego, 9500 Gilman Dr. La Jolla, CA 92093, USA}

@@

 \author{J. Xavier Prochaska}
 \affiliation{Astronomy \& Astrophysics, UC Santa Cruz, 1156 High St., Santa Cruz, CA 95064 USA}

@@

\begin{abstract}
We perform a Very Large Telescope FOcal Reducer and low dispersion Spectrograph 2 (VLT/FORS2) narrowband imaging search around 5 star-forming galaxies at redshift $z=0.67-0.69$ in the Great Observatories Origins Deep Survey South (GOODS-S) field to constrain the radial extent of large-scale outflows traced by resonantly scattered \ion{Mg}{2} emission. The sample galaxies span SFRs in the range $4\msunperyr< SFR < 40\msunperyr$ and have stellar masses $9.9 \lesssim \log M_{*}/M_{\odot} \lesssim 11.0$, and exhibit outflows traced by \ion{Mg}{2} absorption with velocities $\sim150-420\mkms$.
These observations probe unmatched surface brightness limits of 5.81 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ per 1 arcsec$^2$ aperture (at 5$\sigma$ significance).  We do not detect any extended emission around any of the sample galaxies, thus placing sensitive upper limits on the brightness of extended \ion{Mg}{2} emission of $<6.51 \times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ at projected distances $R_{\perp} > 8-21$ kpc. The imaging also resolves the \ion{Mg}{2} absorption observed toward each galaxy spatially, revealing approximately constant absorption strengths across the galaxy disks. 
In concert with radiative transfer models predicting the surface brightness of \ion{Mg}{2} emission for a variety of simple wind morphologies, our detection limits suggest that either (1) the extent of the \ion{Mg}{2}-emitting material in the outflows from these galaxies is limited to $\lesssim 20$ kpc; or (2) the outflows are anisotropic and/or dusty.  
\end{abstract}

@@

\section{Introduction}\label{sec:intro}
Galactic winds play a critical role in regulating the star formation rates and stellar masses of galaxies \citeth{Werk_2014}; however, the physics that powers these winds remains uncertain. Some possible mechanisms have been proposed by theoretical studies that include thermal pressure from core collapse supernovae, radiation pressure from starbursts, and finally cosmic ray pressure (\citethnop{Larson_1974}; \citethnop{Chevalier_1985}; \citethnop{Springel_2003}; \citethnop{Sugahara_2017}). Additionally, the impact galactic winds have on their host galaxies (i.e., their mass and energy content) has remained difficult to constrain with observations.

An accurate picture of the types of galaxies that host outflows comes from numerous absorption line studies of galaxies (\citethnop{Veilleux2005}; \citethnop{Weiner2009}; \citethnop{Martin2012}; \citethnop{Rubin_2014}). Gas flows are detected by measuring the blueshift (outflow) or redshift (inflow) of absorption transitions with respect to the host galaxy systemic velocity. Spectroscopy of galaxies from low to high redshifts probing cold gas ($T \lesssim 10^2$ K) which absorbs in \ion{Na}{1} and cool gas ($T \sim 10^4$ K) in \ion{Mg}{2} has revealed outflows in most galaxies that host active star-formation (e.g. \citethnop{chen2010}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
Even though this technique constrains the radial velocity, column density and covering fraction of the flow, it weakly constrains the overall radial extent and provides no information on the morphology of the gas.

An alternative method that can in principal asses the radial extent and morphology of outflows is to trace the gas in emission. This has been demonstrated using rest-frame optical transitions (i.e H$\alpha$, [\ion{O}{3}], etc) as tracers for winds around nearby starbursts \citep[][]{{Matsubayashi2009,Veilleux2009}} as these transitions can trace the warm shock heated phase of the gas. 
Another transition potentially useful for tracing winds in emission is the \ion{Mg}{2} $\lambda\lambda 2976,2803$ doublet in the rest-frame ultraviolet
\citep[UV;][]{{Weiner2009, Kornei2013}}. While most studies of winds using \ion{Mg}{2} have focused on its absorption kinematics, \cite{Rubin_2011} observed  strong \ion{Mg}{2} emission with a P-Cygni line profile in the spectrum of a strongly star-forming galaxy at redshift $z = 0.694$. In addition, the emission was spatially extended, permitting the first direct measurement of the extent of an outflow ($>$ 7 kpc) in the distant universe.

One proposed production mechanism for such P-Cygni profiles is photon scattering. In this mechanism, \ion{Mg}{2} ions in the region of the wind closest to the observer will absorb continuum photons in the resonant transitions at wavelengths 2796.35\AA\ ($\lambda_{2796}$) and 2803.53\AA\ ($\lambda_{2803}$) \citep{Morton2003}. Once these transitions are excited, they may only decay back to the ground state. If the optical depth of the gas is high, then the gas will resonantly trap the absorbed photons. Because the photons are absorbed in the rest frame of the gas, the absorption will be blueshifted relative to the galaxy's systemic velocity. The \ion{Mg}{2} ions in the section of the wind farthest from the observer will absorb and scatter photons that are redshifted relative to the front portion of the wind. Because the photons are redshifted, the photons travel freely towards the observer through the wind to produce emission at and redward of the systemic velocity of the galaxy (\citethnop{Rubin_2011}, \citethnop{Prochaska_2011}). Since the first detection of \ion{Mg}{2} emission in an individual galaxy by \citet{Rubin_2011}, another detection was reported by \cite{Martin2013}, who observed \ion{Mg}{2} emission that extends $12-18$ kpc from a strongly star-forming galaxy
at $z=0.9392$. \ion{Mg}{2} has also been studied in wide-field galaxy surveys conducted with Keck DEep Imaging Multi-Object Spectrograph (DEIMOS) and VLT Multi Unit Spectroscopic Explorer (MUSE)  (\citethnop{Weiner2009}, \citethnop{Kornei2013},\citethnop{Erb2012}, \citethnop{Feltre2018}). These surveys, which include galaxies with redshifts $ 0.70 < z < 2.30$, find that \ion{Mg}{2} may be detected in pure emission, pure absorption or with P-Cygni profiles and that detections of \ion{Mg}{2} in emission were found to be associated with galaxies of lower stellar mass and bluer spectral slopes.

@@

In this paper, we present the first narrowband imaging of the \ion{Mg}{2} transition around 5 star-forming  galaxies located in the Great Observatories Origins Deep Survey South (GOODS-S; \citethnop{Giavalisco2004})  field at redshift $z \sim 0.7$. 
We use two filters: a  ``line filter" covering the \ion{Mg}{2} doublet, and a ``continuum filter" that is offset from the line filter by ${\sim}47$ \AA.    
The resulting imaging in each filter has a total integration time of 10 hrs. As opposed to 1D spectra, the narrowband imaging constrains the surface brightness, optical depth and radial extent of the wind. These observations allow us to create the first ever high-S/N spatially resolved map of both \ion{Mg}{2} emission and absorption.

In Section \ref{sec:obs_red} we describe our sample of GOODS-S galaxies, supplemental Keck I Low Resolution Imaging Spectrometer (Keck/LRIS) spectra, as well as our VLT/FORS2 observations, image reduction, and absolute flux calibration. We describe our method of continuum subtraction in Section \ref{sec.cont_sub}. Analysis of these data is presented in Section \ref{sec:analysis}, 
including our methods for calculating surface brightness profiles and detection limits for each galaxy, as well as maps of \ion{Mg}{2} equivalent widths.
Section \ref{sec:results} presents results from this analysis. We compare our SB detection limits to previous detections of extended \ion{Mg}{2} emission,  and compare our observations to predictions made by radiative transfer models in Section \ref{sec:discussion}. We conclude this paper in Section \ref{sec:conclusion}.
We adopt a $\Lambda$CDM cosmology with $h_{70} = H_0/(70\ \rm{ km}\ \rm{ s}^{-1}\ \rm{ Mpc}^{-1})$, $\Omega_{\rm{M}}= 0.3$, and $\Omega_{\Lambda} = 0.7$. In this cosmology, 1\arcsec\  is $\approx 7\ \rm kpc$ at $z \sim 0.7$.

\section{Observations and Data Reduction}\label{sec:obs_red}
\subsection{Sample Selection}
Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and $B_{AB}< 23$ in fields with deep Hubble Space Telescope/Advance Camera for Surveys (\emph{HST}/ACS) imaging \citep{Rubin_2014}.  In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}) and the AEGIS survey field \citep[the Extended Groth Strip;][]{Davis2007}.  In inspecting the redshift distribution of the portion of this sample observable from the Southern Hemisphere, we uncovered a narrow peak of nine galaxies in the interval $0.66 < z < 0.68$.  This peak is in fact the global maximum of the distribution, as all other bins of width $\Delta z = 0.02$ have at most four galaxies.  Moreover, there are two narrow interference filters available on VLT/FORS2 centered at $\lambda \sim 4675$ and 4722 \AA\ which cover the \ion{Mg}{2} $\lambda \lambda 2796, 2803$ transition in precisely this redshift interval.  We selected our final sample of five of these galaxies at $0.66 < z < 0.68$ to be close on the sky such that they could be imaged in a single $7' \times 7' $ FORS2 pointing.  
We show color {\it HST}/ACS images of these objects in Figure~\ref{fig:hstims}.

The absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and equivalent widths (EW) $\sim 2-3$ \AA.  Modeling of the galaxy broad-band spectral energy distributions (SED) obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$. The properties of the sample, as well as precise target coordinates taken from \cite{Rubin_2014} are listed in Table \ref{tab:prop}.

\subsection{VLT/FORS2 Observations}
Our narrow-band imaging data were taken in service-mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the \ion{Mg}{2} doublet lines at our sample redshift of $z\sim0.7$ (see Table \ref{tab:filters}). The filter transmission curves are plotted along with each galaxy's spectrum in Figure~\ref{fig:spec_images}.
In the following, we will often refer to the HeII+47 filter as the ``line'' or \ion{Mg}{2} filter and the HeII/3000+48 filter as the ``continuum'' filter.

FORS2 has a native pixel scale of $0.125''$ pixel$^{-1}$ and a field of view of $7'\times7'$.  The data were taken with 
the CCD binned $2\times2$, yielding a pixel scale of $0.25''$ pixel$^{-1}$.
Images of three pointings offset by $0.25\arcmin$ East/West were obtained, with individual exposure times of $\approx$ 1000 sec.  A total of 38  exposures were taken in each filter. 
Our observations were carried out under photometric and thin cloud conditions (program ID: 090.A-0427A). 
The seeing values, given in the header of each image, were derived from zenith observations at 0.5 microns with the Paranal differential image motion monitor \citep[DIMM,][]{Sarazin1990} and include a correction for the airmass and wavelengths of the science observation, as well as a first order correction for the larger site of the Antu mirror. The distribution of these seeing values are shown in Figure \ref{fig.seeing}. The median seeing for the images is $\sim 0.8\arcsec$. Summing the individual exposure times for each filter results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 images.

\begin{figure*}[!ht]
\centering
\includegraphics[scale=.75]{fors2_color_imstamps.pdf}
\caption{Color imaging of our sample galaxies in the \emph{HST}/ACS F435W, F606W, and F775W filters obtained as part of the GOODS survey (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}). Each image is 5\arcsec $\times$ 5\arcsec ( or about $ 35 \rm \ kpc \times 35 \rm \ kpc $) .\label{fig:hstims}}
\end{figure*}

@@

\subsection{Image Reduction}
The imaging data were reduced using custom routines written in \emph{Python}. 
The images were first corrected by subtracting and removing the overscan region of the CCD. 
Then the images were bias-subtracted and flat-fielded using twilight flats.
To improve the flat-fielding essential for detecting faint extended emission across the fields, we further correct for the illumination patterns using night-sky flats. The night-sky flats were produced by combining the unregistered science frames with an average sigma-clipping algorithm after masking out all the objects, and any bad pixels. Each individual image was cleaned of cosmic rays and bad pixels by utilizing the \emph{L.A. Cosmic} algorithm \citep{Dokkum2001}.
The astrometry solutions were calculated via Astrometry.net \citep{Lang}, and yield a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$. Before image stacking, we ran each frame through \emph{SExtractor} \citeth{Bertin} to create a root mean square (RMS) map of each science image.

The final stacked image for each filter is obtained using \emph{SWarp} \citeth{Bertin}.
Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. 
We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted \citep[e.g.,][]{Battaia_2015}. 
The frames, after background-subtraction, are resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
The images are weighted by the night-flat image and then  average-combined to increase the signal-to-noise of any \ion{Mg}{2} emission. Additionally, \emph{SWarp} generates stacked RMS images by propagating the error images for each science frame.
Our final stacked images in each filter are shown in Figure~\ref{fig:stacked_image} with the target galaxies indicated.

\begin{table*}[t]
\centering
\caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
determined from analysis of the supplemental Keck/LRIS spectra.}
\begin{tabular}{llllllll} \hline \hline
Object\footnote{ Name in parenthesis to be used as shorthand for the objects throughout the remainder of the paper. } & R.A. & Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW$_{\rm{obs}}$(\AA) & $\tau_V$\footnote{ Total V-band optical depth of dust as estimated by SED fitting with MAGPHYS. }\smallskip      \\ \hline 
J033225.26-274524.0 (J.26)      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$ &  $1.227_{-0.20}^{+1.54}$\\

@@

J033230.57-274518.2  (J.57)    & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ & $1.262_{-0.40}^{+1.23}$ \\
\hline 
\end{tabular}
\tablenotemark{}
\tablenotetext{}{\textit{Note} - The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SED with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}}
\label{tab:prop}
\end{table*}

\begin{table}[h!]
\caption{Filter properties  and exposure times of the VLT/FORS2 observations. The width of the transmission curves ($\Delta\lambda$) are calculated by convolving the transmission curve with the total wavelength range of the filter. These values differ slightly from those reported by the European Space Observatory. }
\begin{tabular}{llllll} \hline \hline 
Filter & $\lambda_{\rm{eff}}$(\AA)\footnote{$ \lambda_{\rm{eff}}$ is the effective wavelength of the filter transmission curve.} & $\Delta\lambda$(\text{\AA})    & $N$\footnote{ Total number of images.}   & $T(s)$\footnote{ Total exposure time.} & $S$\footnote{ S, the sensitivity of the filter, is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$ .}\smallskip  \\ \hline 
HeII+47  & 4675.21 & 50.11 & 38  & 35,959 & 2.45 \\
HeII/3000+48 & 4722.46  & 44.82 & 38 &   36,937 & 2.40  \\ \hline
\end{tabular}
\label{tab:filters}
\end{table}

>>>>

\begin{document}
\title{A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies }
\author{Ryan Rickards Vaught}
\affiliation{Department of Astronomy, San Diego State University, San Diego, CA 92182}
\affiliation{Department of Physics, University of California, San Diego, 9500 Gilman Dr., La Jolla, CA 92093, USA}

@@

 \author{J. Xavier Prochaska}
 \affiliation{Department of Astronomy \& Astrophysics, University of California, 1156 High St., Santa Cruz, CA 95064 USA}

@@

\begin{abstract}
We perform a Very Large Telescope FOcal Reducer and low dispersion Spectrograph 2 (VLT/FORS2) narrowband imaging search around 5 star-forming galaxies at redshift $z=0.67-0.69$ in the Great Observatories Origins Deep Survey South (GOODS-S) field to constrain the radial extent of large-scale outflows traced by resonantly scattered \ion{Mg}{2} emission. The sample galaxies span star formation rates in the range $4\msunperyr< \mathrm{SFR} < 40\msunperyr$ and have stellar masses $9.9 \lesssim \log M_{*}/M_{\odot} \lesssim 11.0$, and exhibit outflows traced by \ion{Mg}{2} absorption with velocities $\sim150-420\mkms$.
These observations are uniquely sensitive, reaching surface brightness limits of 5.81 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ per 1 arcsec$^2$ aperture (at 5$\sigma$ significance).  We do not detect any extended emission around any of the sample galaxies, thus placing  upper limits on the brightness of extended \ion{Mg}{2} emission of $<6.51 \times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ at projected distances $R_{\perp} > 8-21$ kpc. The imaging also resolves the \ion{Mg}{2} absorption observed toward each galaxy spatially, revealing approximately constant absorption strengths across the galaxy disks. 
In concert with radiative transfer models predicting the surface brightness of \ion{Mg}{2} emission for a variety of simple wind morphologies, our detection limits suggest that either (1) the extent of the \ion{Mg}{2}-emitting material in the outflows from these galaxies is limited to $\lesssim 20$ kpc; or (2) the outflows are anisotropic and/or dusty.  
\end{abstract}

@@

\section{Introduction}\label{sec:intro}
Galactic winds play a critical role in regulating the star formation rates and stellar masses of galaxies \citeth{Werk_2014}; however, the physics that powers these winds remains uncertain. Some possible mechanisms have been proposed by theoretical studies that include thermal pressure from core collapse supernovae, radiation pressure from starbursts, and finally cosmic ray pressure (e.g., \citethnop{Larson_1974}; \citethnop{Chevalier_1985}; \citethnop{Springel_2003}; \citethnop{Sugahara_2017}). Additionally, the impact galactic winds have on their host galaxies (i.e., their mass and energy content) has remained difficult to constrain with observations.

An accurate picture of the types of galaxies that host outflows comes from numerous absorption line studies of galaxies (e.g., \citethnop{Veilleux2005}; \citethnop{Weiner2009}; \citethnop{Martin2012}; \citethnop{Rubin_2014}). Gas flows are detected by measuring the blueshift (outflow) or redshift (inflow) of absorption transitions with respect to the host galaxy systemic velocity. Spectroscopy of galaxies from low to high redshifts probing cold gas ($T \lesssim 10^2$ K) which absorbs in \ion{Na}{1} and cool gas ($T \sim 10^4$ K) absorbing \ion{Mg}{2} has revealed outflows in most galaxies that host active star formation (e.g. \citethnop{chen2010}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
While this technique is useful for constraining the radial velocity, column density and covering fraction of the flow, it weakly constrains the overall radial extent and provides little information on the morphology of the gas.

An alternative method that can in principle assess the radial extent and morphology of outflows is to trace the gas in emission. This has been demonstrated using rest-frame optical transitions (i.e., H$\alpha$, [\ion{O}{3}]) as tracers for winds around nearby starbursts \citep[e.g.,][]{{Matsubayashi2009,Veilleux2009}} as these transitions can trace the warm shock-heated phase of the gas. 
Another transition potentially useful for tracing winds in emission is the \ion{Mg}{2} $\lambda\lambda 2976,2803$ doublet in the rest-frame ultraviolet
\citep[UV;][]{{Weiner2009, Kornei2013}}. While most studies of winds using \ion{Mg}{2} have focused on its absorption kinematics, \cite{Rubin_2011} observed  strong \ion{Mg}{2} emission with a P-Cygni line profile in the spectrum of a strongly star-forming galaxy at redshift $z = 0.694$. In addition, the emission was spatially extended, permitting the first direct measurement of the extent of an outflow ($\gtrsim$ 7 kpc) in the distant universe.

One proposed production mechanism for such P-Cygni profiles is photon scattering. In this mechanism, \ion{Mg}{2} ions in the region of the wind closest to the observer will absorb continuum photons in the resonant transitions at wavelengths 2796.35\AA\ ($\lambda_{2796}$) and 2803.53\AA\ ($\lambda_{2803}$) \citep{Morton2003}. Once these transitions are excited, they may only decay back to the ground state. If the optical depth of the gas is high, then the gas will resonantly trap the absorbed photons. Because the photons are absorbed in the rest frame of the gas, the absorption will be blueshifted relative to the galaxy's systemic velocity. The \ion{Mg}{2} ions in the section of the wind farthest from the observer will absorb and scatter photons that are redshifted relative to the front portion of the wind. Because the photons are redshifted, the photons travel freely towards the observer through the wind to produce emission at and redward of the systemic velocity of the galaxy (\citethnop{Rubin_2011}, \citethnop{Prochaska_2011}).

Since the first detection of \ion{Mg}{2} emission in an individual galaxy by \citet{Rubin_2011}, another detection was reported by \cite{Martin2013}, who observed \ion{Mg}{2} emission that extends $12-18$ kpc from a strongly star-forming galaxy
at $z=0.9392$. \ion{Mg}{2} has also been studied in wide-field galaxy surveys conducted with the Keck DEep Imaging Multi-Object Spectrograph (DEIMOS) and the VLT Multi Unit Spectroscopic Explorer (MUSE)  (\citethnop{Weiner2009}, \citethnop{Kornei2013}, \citethnop{Erb2012}, \citethnop{Feltre2018}). These surveys, which include galaxies with redshifts $ 0.70 < z < 2.30$, find that \ion{Mg}{2} may be detected in pure emission, pure absorption or with P-Cygni profiles and that detections of \ion{Mg}{2} in emission were found to be more commonly associated with galaxies of lower stellar mass and with bluer spectral slopes.

@@

In this paper, we present the first narrowband imaging of the \ion{Mg}{2} transition around 5 star-forming  galaxies located in the Great Observatories Origins Deep Survey South (GOODS-S; \citethnop{Giavalisco2004})  field at redshift $z \sim 0.7$. 
We use two filters: a  ``line filter" covering the \ion{Mg}{2} doublet, and a ``continuum filter" that is offset from the line filter by ${\sim}47$ \AA.    
The resulting imaging in each filter has a total integration time of 10 hrs. As opposed to 1D spectra, the narrowband imaging constrains the surface brightness and radial extent of the wind. These observations allow us to create the first ever high-S/N spatially resolved map of both \ion{Mg}{2} emission and absorption.

In Section \ref{sec:obs_red} we describe our sample of GOODS-S galaxies, supplemental Keck I Low Resolution Imaging Spectrometer (Keck/LRIS) spectra, as well as our VLT/FORS2 observations, image reduction, and absolute flux calibration. We describe our method of continuum subtraction in Section \ref{sec.cont_sub}. Analysis of these data is presented in Section \ref{sec:analysis}, 
including our methods for calculating surface brightness profiles and detection limits for each galaxy, as well as maps of \ion{Mg}{2} equivalent widths.
Section \ref{sec:results} presents results from this analysis. We compare our SB detection limits to previous detections of extended \ion{Mg}{2} emission,  and compare our observations to predictions made using radiative transfer models in Section \ref{sec:discussion}. We conclude this paper in Section \ref{sec:conclusion}.
We adopt a $\Lambda$CDM cosmology with $h_{70} = H_0/(70\ \rm{ km}\ \rm{ s}^{-1}\ \rm{ Mpc}^{-1})$, $\Omega_{\rm{M}}= 0.3$, and $\Omega_{\Lambda} = 0.7$. In this cosmology, 1\arcsec\  is $\approx 7\ \rm kpc$ at $z \sim 0.7$.

\section{Observations and Data Reduction}\label{sec:obs_red}
\subsection{Sample Selection}
Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and rest-frame $B$-band magnitudes $B_{\rm AB}< 23$ in fields with deep Hubble Space Telescope/Advanced Camera for Surveys (\emph{HST}/ACS) imaging \citep{Rubin_2014}.  In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}) and the AEGIS survey field \citep[the Extended Groth Strip;][]{Davis2007}.  In inspecting the redshift distribution of the portion of this sample observable from the Southern Hemisphere, we uncovered a narrow peak of nine galaxies in the interval $0.66 \lesssim z \lesssim 0.68$.  This peak is in fact the global maximum of the distribution, as all other bins of width $\Delta z = 0.02$ have at most four galaxies.  Moreover, there are two narrow interference filters available on VLT/FORS2 centered at $\lambda \sim 4675$ \AA\ and 4722 \AA\ which cover the \ion{Mg}{2} $\lambda \lambda 2796, 2803$ transition in precisely this redshift interval.  We selected our final sample of five of these galaxies %at %$0.66 < z < 0.68$ 
to be close on the sky such that they could be imaged in a single $7' \times 7' $ FORS2 pointing.  
We show color {\it HST}/ACS images of these objects in Figure~\ref{fig:hstims}.

The absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and equivalent widths (EW) $\sim 2-3$ \AA.  Modeling of the galaxy broad-band spectral energy distributions (SEDs) obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$. The properties of the sample, as well as precise target coordinates taken from \cite{Rubin_2014}, are listed in Table \ref{tab:prop}.

\subsection{VLT/FORS2 Observations}
Our narrow-band imaging data were taken in service mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the \ion{Mg}{2} doublet lines at our sample redshift of $z\sim0.7$ (see Table \ref{tab:filters}). The filter transmission curves are plotted along with each galaxy's spectrum in Figure~\ref{fig:spec_images}.
In the following, we will often refer to the HeII+47 filter as the ``line'' or \ion{Mg}{2} filter and the HeII/3000+48 filter as the ``continuum'' filter.

FORS2 has a native pixel scale of $0.125''$ pixel$^{-1}$ and a field of view of $7'\times7'$.  The data were taken with 
the CCD binned $2\times2$, yielding a pixel scale of $0.25''$ pixel$^{-1}$.
Images of three pointings offset by $0.25\arcmin$ East/West were obtained, with individual exposure times of $\approx$ 1000 sec.  A total of 38  exposures were taken in each filter. 
Our observations were carried out under photometric and thin cloud conditions (program ID: 090.A-0427A). 
The seeing values, given in the header of each image, were derived from zenith observations at 0.5 micron with the Paranal differential image motion monitor \citep[DIMM;][]{Sarazin1990} and include a correction for the airmass and wavelengths of the science observations, as well as a first order correction for the larger size of the Antu mirror. The distribution of these seeing values is shown in Figure \ref{fig.seeing}. The median seeing for the images is $\sim 0.8\arcsec$. Summing the individual exposure times for each filter results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 images.

\begin{figure*}[!ht]
\centering
\includegraphics[scale=.75]{fors2_color_imstamps.pdf}
\caption{Color imaging of our sample galaxies in the \emph{HST}/ACS F435W, F606W, and F775W filters obtained as part of the GOODS survey (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}). Each image is 5\arcsec $\times$ 5\arcsec\ (or about $35 \rm \ kpc \times 35 \rm \ kpc$).\label{fig:hstims}}
\end{figure*}

@@

\subsection{Image Reduction}
The imaging data were reduced using custom routines written in \emph{Python}. 
The images were first corrected by subtracting and removing the overscan region of the CCD. 
Then the images were bias-subtracted and flat-fielded using twilight flats.
%%% KHRR -- adjusting the following to be different from FAB's words
%To improve the flat-fielding essential for detecting faint extended emission across the %fields, we further correct for the illumination patterns using night-sky flats. The %night-sky flats were produced by combining the unregistered science frames with an %average sigma-clipping algorithm after masking out all the objects, and any bad pixels. 
%%%
An additional flat-fielding correction was performed using night-sky flats to improve our sensitivity to faint extended emission.  The night-sky flats were produced by first masking out all objects and bad pixels in the science frames, and then combining them using an average sigma-clipping algorithm.
Each individual image was cleaned of cosmic rays and bad pixels by utilizing the \emph{L. A. Cosmic} algorithm \citep{Dokkum2001}.
The astrometry solutions were calculated via Astrometry.net \citep{Lang}, and yield a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$. Before image stacking, we ran each frame through \emph{SExtractor} \citeth{Bertin} to create a root mean square (RMS) map of each science image.

The final stacked image for each filter is obtained using \emph{SWarp} \citeth{Bertin}.
Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. 
We chose the mesh size to be large enough such that any extended emission is not mistakenly subtracted \citep[e.g.,][]{Battaia_2015}. 
The frames, after background-subtraction, are resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
The images are weighted by the night-flat image and then  average-combined to increase the signal-to-noise of any \ion{Mg}{2} emission. Additionally, \emph{SWarp} generates stacked RMS images by propagating the error images for each science frame.
Our final stacked images in each filter are shown in Figure~\ref{fig:stacked_image} with the target galaxies indicated.

\begin{table*}[t]
%\centering
\caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
determined from analysis of the supplemental Keck/LRIS spectra.}
\begin{tabular}{llllllll} \hline \hline
Object\footnote{ Name in parenthesis to be used as shorthand for the objects throughout the remainder of the paper. } & R.A. & Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW$_{\rm{obs}}$(\AA) & $\tau_V$\footnote{ Total V-band optical depth of dust as estimated by SED fitting with MAGPHYS. }\smallskip      \\ \hline 
J033225.26-274524.0 (J.26)      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$ &  $1.227_{-0.20}^{+1.54}$\\

@@

J033230.57-274518.2  (J.57)    & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ & $1.262_{-0.40}^{+1.23}$ \\
\hline 
\end{tabular}
\tablenotemark{}
\tablenotetext{}{\textit{Note} - The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}}
\label{tab:prop}
\end{table*}

\begin{table}[h!]
\caption{Filter properties  and exposure times of the VLT/FORS2 observations. The widths of the transmission curves ($\Delta\lambda$) are calculated by convolving the transmission curves over the total wavelength range of each filter. These values differ slightly from those reported by the European Southern Observatory. }
\begin{tabular}{llllll} \hline \hline 
Filter & $\lambda_{\rm{eff}}$(\AA)\footnote{$ \lambda_{\rm{eff}}$ is the effective wavelength of the filter transmission curve.} & $\Delta\lambda$(\text{\AA})    & $N$\footnote{ Total number of images.}   & $T(s)$\footnote{ Total exposure time.} & $S$\footnote{ S, the sensitivity of the filter, is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$ .}\smallskip  \\ \hline 
HeII+47  & 4675.21 & 50.11 & 38  & 35,959 & 2.45 \\
HeII/3000+48 & 4722.46  & 44.82 & 38 &   36,937 & 2.40  \\ \hline
\end{tabular}
\label{tab:filters}
\end{table}
